greta.Rmd

### 2019-08-07 notebook/ghost-fit.Rmd
store indices only

lows <- means %>% dplyr::slice(1:10) %>% pull(reps)
highs <- means %>% dplyr::slice((n()-10):n()) %>% pull(reps)
coding <- function(reps) case_when(
  reps %in% lows ~ "low",
  reps %in% highs ~ "high"
)
extremes <- data %>% mutate(coding = coding(reps)) %>% na.omit()

write_csv(extremes, "../data/extremes.csv.xz")
extremes %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

>>>>

lows <- means %>% dplyr::slice(1:10) %>% pull(reps)
highs <- means %>% dplyr::slice((n()-9):n()) %>% pull(reps)
coding <- function(reps) case_when(
  reps %in% lows ~ "low",
  reps %in% highs ~ "high"
)
extremes <- data %>% mutate(coding = coding(reps)) %>% na.omit()

write_csv(data.frame(lows=lows,highs=highs), "../data/extremes.csv.xz")
extremes %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)
